Probing internal structure of distant quasars using Microlensing

### 2014-03-21 paper1/intro.tex

\section{introduction}
AMore than half a century after their discovery, quasars still maintain the interest of a productive part of the astrophysical community. Although several mechanisms have been proposed 
to explain how such systems function a single mechanism is widely accepted at the present time. The model was first proposed by Salpeter in 1964 (citation), folowed by Zel'dovich and Novikov in the same year (citation) and Lynden-Bell five years later. The present name of the model is the Super-Massive Black Hole (SMBH) paradigm.\\

>>>>

\section{introduction}
More than half a century after their discovery, quasars still maintain the interest of a productive part of the astrophysical community. Although several mechanisms have been proposed 
to explain how such systems function a single mechanism is widely accepted at the present time. The model was first proposed by Salpeter in 1964 (citation), folowed by Zel'dovich and Novikov in the same year (citation) and Lynden-Bell five years later. The present name of the model is the Super-Massive Black Hole (SMBH) paradigm.\\
